---
title: 'BGApredictor Report'
author: 'Operator/Analyst: Name Surname'
date: 
output: pdf_document
params:
  plotSVM1: 'NULL'
  plotSVM2: 'NULL'
  prova1SVM: 'NULL'
  prova2SVM: 'NULL'
  prova3SVM: 'NULL'
  
always_allow_html: true
header-includes:
  - \usepackage{fancyhdr}
---

\addtolength{\headheight}{1.0cm}  
\pagestyle{fancyplain} 
\rhead{\includegraphics[height=1.2cm]{C:/Users/eugen/Documents/Racis/RIS_Roma/Sez_Biologia/App_etnia/App_articolo/image_2.png}} 
\lhead{\includegraphics[height=1.2cm]{C:/Users/eugen/Documents/Racis/RIS_Roma/Sez_Biologia/App_etnia/App_articolo/image_1.png}} 
\renewcommand{\headrulewidth}{0pt} 


# Support Vector Machines (SVM) Model
<br/><br/>
The SVM model that has been calculated on the tested reference populations, before evaluating the subject **`r rownames(params$prova1SVM)`**, provided the following classification results:
<br/><br/>

```{r, echo=FALSE}
params[["plotSVM1"]]
```


The classification of the subject **`r rownames(params$prova1SVM)`** showed the following SVM prediction values:
<br/><br/>

```{r, echo=FALSE}
params[["plotSVM2"]]
```

\pagebreak

# Summary of the results
<br/><br/>
The subject **`r rownames(params$prova1SVM)`** has been classified, as follows:
<br/><br/>

```{r, echo=FALSE}
params[["prova1SVM"]]
params[["prova2SVM"]]
```

